A GPU Implementation of Capon for an Active Sonar System

### 2012-05-07 ECUA2012/gpu_capon_ecua2012.tex
la2pdf commit - 2012:05:07	12:23:20	(Mon 7.May)

\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{gfx/benchmark.pdf}
\caption{Capon benchmarks. An 55\,kpx image processed with $M=32$ channels and $d=2\%$ diagonal loading. }\label{benchmarks}
\end{figure}

@@

Figure \ref{holmengraa} demonstrates the Capon beamformer's ability to suppress interference and achieve better detail resolution. Compared the \gls{DAS} beamformer, the ship edges come out as sharper, and the shadows are less noisy. But while \gls{DAS} processed this 1.3Mpx image in milliseconds, our Matlab implementation of Capon needed minutes.

Figure \ref{benchmarks} shows how a \gls{GPU} can be used to improve matters.  The test image used here was 55kpx,   and the \gls{} hence the runtimes are seen are   much smaller than the Holmengraa image, but the relative performance increase seen when accelerating the algorithm with a \gls{GPU} is still accurate.

>>>>

\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{gfx/benchmark.pdf}
\caption{Capon benchmarks. \protect\newline A 55\,kpx image processed with $M=32$ channels and $d=2\%$ diagonal loading.}\label{benchmarks}
\end{figure}

@@

Figure \ref{holmengraa} demonstrates the Capon beamformer's ability to suppress interference and achieve better detail resolution. Compared the \gls{DAS} beamformer, the ship's edges come out as sharper, and the shadows are less noisy. But while \gls{DAS} processed this 1.3Mpx image in milliseconds, our Matlab implementation of Capon needed minutes.

As Figure \ref{benchmarks} illustrates, using a \gls{GPU} improve matters.  and the \gls{} hence the runtimes are seen are   much smaller than the Holmengraa image, but the relative performance increase seen when accelerating the algorithm with a \gls{GPU} is still accurate.
